---
title: "Progress Report"
author: "Hidefumi Watanabe"
date: "8/9/2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal of This Week
Import from CA API to R statnete format

## Progress of This Week
1. Load json output of CA into R using rlist
   - Json format of CA whole record is a little different from json format of CA individual record.
   - Obtain whole record of CA concepts
   - Obtain individual record using whole concept_id
2. Export rlist format to statnet format "network"
   - create adjacent matirix using as.sociomatrix
   - create plot

## Output
ons_20180809.R

```{r ons, echo = TRUE, eval=FALSE}
### creating concept_id list
library("rlist")
url <- "http://cognitiveatlas.org/api/v-alpha/concept?"
all <- list.load(url)
id_list <- list.map(all, id)

### creating API url list using concept_id
base <- "http://cognitiveatlas.org/api/v-alpha/concept?id="
url_list <- list.apply(id_list, function(x){paste(base,x,sep="")})

### creating list by concept
edge_list <- list.apply(url_list,function(x){
  con <- list.load(x) # con stands for "concept"
  src_name <- con$name
  edge_list <- list.select(con$relationships,src_name,dst_name = name, relationship)
  list.stack(edge_list)
})
edge_df <- list.rbind(edge_list)

### saving data frame as CSV
write.csv(edge_df[,1:2], file = "MyData.csv",
          row.names = FALSE)
net.edge <- read.csv(file="MyData.csv")
net_import <- network(net.edge,
                      matrix.type="edgelist")

### creating plot
op <- par(mar = rep(0,4), mfrow=c(1,2))
plot(net_import,mode="fruchtermanreingold",vertex.cex=1.5)
par(op)

### get vertex attribute
get.vertex.attribute(net_import,"src_name")
### creating adjacent matrix
adjacent <- as.sociomatrix(net_import)
write.csv(adjacent, file = "adjacent.csv")

### count relation
library("dplyr")
edge_df %>% group_by(relationship) %>% summarize(count = n())

### centrality analysis
degree(net_import,gmode="graph")
closeness(net_import,gmode="graph")
betweenness(net_import,gmode="graph")
```


Plot sample:
```{r, echo = FALSE, eval=TRUE, warning=FALSE,error=FALSE, message=FALSE}
library("statnet")
net.edge <- read.csv(file="~/MyData.csv")
net_import <- network(net.edge,
                      matrix.type="edgelist")

op <- par(mar = rep(0,4), mfrow=c(1,2))
plot(net_import,mode="fruchtermanreingold",vertex.cex=1.5)
par(op)
```

