---
title: "Progress Report"
author: "Hidefumi Watanabe"
date: "8/24/2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal of This Week
Create network plot using centrality

## Progress of This Week
1. rescale function to represent centrality

## Output
centrality.R

```{r ons, echo = TRUE, eval=FALSE}
rescale <- function(nchar, low, high){
  min_d <- min(nchar)
  max_d <- max(nchar)
  rscl <- ((high-low)*(nchar-min_d)) / (max_d-min_d)+low
  rscl
}

op <- par(mar = rep(0,4), mfrow=c(1,2))
plot(net_import,vertex.cex=rescale(deg,1,7))
par(op)

op <- par(mar = rep(0,4), mfrow=c(1,2))
plot(net_import,vertex.cex=rescale(bet,1,7))
par(op)
```


Plot sample:
```{r, echo = FALSE, eval=TRUE, warning=FALSE,error=FALSE, message=FALSE}
library("statnet")
net.edge <- read.csv(file="~/MyData.csv")
net_import <- network(net.edge,
                      matrix.type="edgelist")

rescale <- function(nchar, low, high){
  min_d <- min(nchar)
  max_d <- max(nchar)
  rscl <- ((high-low)*(nchar-min_d)) / (max_d-min_d)+low
  rscl
}

deg = degree(net_import,gmode="graph",cmode="indegree")
bet = betweenness(net_import,gmode="graph")

op <- par(mar = rep(0,4), mfrow=c(1,2))
plot(net_import,vertex.cex=rescale(deg,1,7))
par(op)

op <- par(mar = rep(0,4), mfrow=c(1,2))
plot(net_import,vertex.cex=rescale(bet,1,7))
par(op)
```

## Remaining Task
1. Show label only on significant function

## Discussion
Discussed the following possible two scenario;
1. Analyzing CA replicateing "Semantic Network Analysis of Ontologies" as discussion on mathematical understanding of CA
2. Comparing text-mining based network analysis and ontology-relationship based network structure using "Mapping the Semantic Structure of Cognitive Neuroscience" as discussion on neuroscientific investigation
###Conclusion
Option2 is better to pursue.
