---
title: "Progress Report"
author: "Hidefumi Watanabe"
date: "9/11/2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Progress of this week
Creating Ontology-based network map using Concept Class

```{r, echo = FALSE, eval=TRUE, warning=FALSE,error=FALSE, message=FALSE}
library("statnet")
library("dplyr")
library(RColorBrewer)

setwd("~/work/ONS/")
net.relation <- read.csv(file="MyData.csv")
class_map <- read.csv(file="MyClass.csv",stringsAsFactors=FALSE)

net_import <- network(net.relation,
                      directed = FALSE,
                      matrix.type="edgelist")

df_c_attribute <- data.frame(
  src_name = net_import %v% 'vertex.names'
)
df_c_merged <- df_c_attribute %>% left_join(class_map,by="src_name")
net_import <- set.vertex.attribute(net_import,"class",df_c_merged[,2])

rescale <- function(nchar, low, high){
  min_d <- min(nchar)
  max_d <- max(nchar)
  rscl <- ((high-low)*(nchar-min_d)) / (max_d-min_d)+low
  rscl
}

net <- network(net_import)

df.cent <- data.frame(
  con = net %v% 'vertex.names',
  cla = net %v% 'class',
  deg = degree(net_import,gmode="graph",cmode="indegree"),
  cls = closeness(net_import,gmode="graph"),
  bet = betweenness(net_import,gmode="graph"),
  evc = evcent(net_import,gmode="graph")
)

### legend_class
my_pal <- brewer.pal(10,"Paired")
classcat <- as.factor(get.vertex.attribute(net_import,"class"))
op <- par(mar=c(2,0,2,0))
plot(net_import,vertex.cex=rescale(df.cent$bet,1,7),vertex.col=my_pal[classcat],main="Concepts colored by Class")
legend("bottomleft",legend=levels(classcat),
       col=my_pal,pch=19, pt.cex=0.5, bty="n",cex=0.5,
       title="Concept Class")
par(op)

####
bet_rank <- df.cent %>% arrange(desc(bet)) %>% head(15)

library("rlist")
### creating ID List
url <- "http://cognitiveatlas.org/api/v-alpha/concept?"
all <- list.load(url)
all_df <- list.stack(all, fill=TRUE)

class_name <- read.csv("class_name.csv",header = TRUE)
class_df <- all_df[,c("name","id_concept_class")]
class_merged <- left_join(class_df,class_name,by="id_concept_class")
class_table_all <- class_merged %>% group_by(class_name) %>% summarize(count = n()) #%>% arrange(desc(count))
class_table_rel <- df_c_merged %>% group_by(name) %>% summarize(count = n()) #%>% arrange(desc(count))
class_table <- data.frame(
  class = as.vector(class_table_all[,1]),
  a_count = class_table_all[,2],
  v_count =class_table_rel[,2]
)
colnames(class_table) <- c("class","a_count","v_count")
class_table <- class_table %>% arrange(desc(a_count))
class_table <- mutate(class_table, ratio = v_count/a_count * 100)

library(knitr)
kable(bet_rank[,c(1,2,3,5)])
kable(class_table)
```

## Comment
1. "working memory","memory"", "perception"", "recognition"",and "decision making"" are five major items by betweenness centrality
2. "Perception", "Learning and Memory","Executive/Cognitive Control", and "Reasoning and decision making" are four major classes which located on the center of the network.
3. Values of "v_count(connected items)/a_count(all items)" are varied in the classes.
4. Some of items are intricatelly located across the class.(ex. Learning and Memory) 

## Questions
1. Why are relations of some concepts blank?
2. How were the classes determined?
3. How were the class of concepts determined?
4. How can betweenness centrality between TM-based and Ontology-based be normalized?
5. Why are the closeness centrality of all concepts zero?

## Goal at the moment
1. Cluster concepts by relations among concepts
2. Classify concepts by relations among concepts
3. Infer or verify relations by concept-task relation (MEASUREDBY value)

## Next Step
1. Creating subgroups using igraph instead of statnet to generate clusters
2. Exploring affiliation network to generate concept-task ties

## Next major task
1. merger algorithm of CA concepts to compare with TM-based betweenness



