---
title: "Progress Report"
author: "Hidefumi Watanabe"
date: "9/4/2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal
1. Comparison of conceptual betweenness between TM-based and Ontology-based
2. Comparison of network map between TM-based and Ontology-based
3. Creating functional network using ontology

## Goal of this week
1. Comparison of conceptual betweenness between TM-based and Ontology-based

## Progress of This Week
1. creating TOP30 concept by major centrality
2. Represent class of concept

## Output
centrality.R

```{r ons, echo = TRUE, eval=FALSE}
net <- network(net_import)

df.cent <- data.frame(
  con = net %v% 'vertex.names',
  deg = degree(net_import,gmode="graph",cmode="indegree"),
  cls = closeness(net_import,gmode="graph"),
  bet = betweenness(net_import,gmode="graph"),
  evc = evcent(net_import,gmode="graph")
)

deg_rank <- df.cent %>% arrange(desc(deg)) %>% head(30)
bet_rank <- df.cent %>% arrange(desc(bet)) %>% head(30)
evc_rank <- df.cent %>% arrange(desc(evc)) %>% head(30)
cent_rank <- cbind(deg_rank[,c(1,2)],bet_rank[,c(1,4)],evc_rank[,c(1,5)])

library("rlist")
### creating ID List
url <- "http://cognitiveatlas.org/api/v-alpha/concept?"
all <- list.load(url)
all_df <- list.stack(all, fill=TRUE)

class_name <- read.csv("class_name.csv",header = TRUE)
class_df <- all_df[,c("name","id_concept_class")]
class_merged <- left_join(class_df,class_name,by="id_concept_class")
class_table <- class_merged %>% group_by(class_name) %>% summarize(count = n()) %>% arrange(desc(count))
```


Plot sample:
```{r, echo = FALSE, eval=TRUE, warning=FALSE,error=FALSE, message=FALSE}
library("statnet")
library("dplyr")
net.edge <- read.csv(file="~/MyData.csv")
net_import <- network(net.edge,
                      matrix.type="edgelist")

net <- network(net_import)

df.cent <- data.frame(
  con = net %v% 'vertex.names',
  deg = degree(net_import,gmode="graph",cmode="indegree"),
  cls = closeness(net_import,gmode="graph"),
  bet = betweenness(net_import,gmode="graph"),
  evc = evcent(net_import,gmode="graph")
)

deg_rank <- df.cent %>% arrange(desc(deg)) %>% head(30)
bet_rank <- df.cent %>% arrange(desc(bet)) %>% head(30)
evc_rank <- df.cent %>% arrange(desc(evc)) %>% head(30)
cent_rank <- cbind(deg_rank[,c(1,2)],bet_rank[,c(1,4)],evc_rank[,c(1,5)])

library("rlist")
### creating ID List
url <- "http://cognitiveatlas.org/api/v-alpha/concept?"
all <- list.load(url)
all_df <- list.stack(all, fill=TRUE)

class_name <- read.csv("class_name.csv",header = TRUE)
class_df <- all_df[,c("name","id_concept_class")]
class_merged <- left_join(class_df,class_name,by="id_concept_class")
class_table <- class_merged %>% group_by(class_name) %>% summarize(count = n()) %>% arrange(desc(count))

library(knitr)
kable(cent_rank)
kable(class_table)

```

## Remaining Task
1. merger algorithm of concepts to compare with TM-based betweenness
2. Add class to the conceptual network map in order to explore NA class
3. Verify the idea to devise an algorithm to determine class by relationship of concept

## Other learnings and questions
1. Learning: adjacent matrix of concept is undirected.s
2. closeness betweenness of all concepts is zero. 

