---
title: "Progress Report"
author: "Hidefumi Watanabe"
date: "9/16/2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Progress of this week
1. Visualizing the feature of concepts and class
2. Creating clusters using various clustering algorithm

## Visualization
```{r, echo = FALSE, eval=TRUE, warning=FALSE,error=FALSE, message=FALSE,results='asis'}
library("dplyr")
setwd("~/pj/ONS/dat/")

library(ggplot2)
##### class count
base_df <- read.csv(file="MyBase.csv")
class_map <- read.csv(file="MyClass.csv",stringsAsFactors=FALSE)
base_merged <- base_df %>% left_join(class_map, by="src_name")

ggplot(base_merged,aes(name,fill = relflg)) +
  geom_bar() +
  labs(title = "# of concepts by relation_flag(TRUE:relations exist)") +
  theme(axis.text.x = element_text(angle = -90, size = 6))
#detach(package:igraph)
library(statnet)
library(RColorBrewer)

net.relation <- read.csv(file="MyData.csv")
net_import <- network(net.relation,
                      directed = FALSE,
                      matrix.type="edgelist")
df_c_attribute <- data.frame(
  src_name = net_import %v% 'vertex.names'
)
df_c_merged <- df_c_attribute %>% left_join(class_map,by="src_name")
net_import %v% 'class' <- as.vector(df_c_merged[,2])

### Visualization
df.cent <- read.csv(file="MyCenter.csv")
#### ggplot
# use display.brewer.all() to see all options

##### deg & bet map
deg_t <- 40
bet_t <- 10000

ggplot(df.cent, aes(deg,bet)) +
  geom_point() +
  facet_wrap(~cla) +
  labs(title = "Significant Concepts measured by Deg & Bet") +
  geom_text(
    data=subset(df.cent, deg > deg_t | bet > bet_t),
    aes(deg,bet,label=con))

#### Network Map
rescale <- function(nchar, low, high){
  min_d <- min(nchar)
  max_d <- max(nchar)
  rscl <- ((high-low)*(nchar-min_d)) / (max_d-min_d)+low
  rscl
}

####
my_pal <- brewer.pal(10,"Paired")
classcat <- as.factor(get.vertex.attribute(net_import,"class"))
#### without label & with rescale
op <- par(mar=c(2,0,2,0))
plot(net_import,vertex.cex=rescale(df.cent$bet,1,7),
     vertex.col=my_pal[classcat],
     label = ifelse(betweenness(net_import,gmode="graph")>bet_t, net_import %v% 'vertex.names',""),
     displaylabels=TRUE,
     main="Concepts colored by Class")
### legend_class
legend("bottomleft",legend=levels(classcat),
       col=my_pal,pch=19, pt.cex=0.5, bty="n",cex=0.5,
       title="Concept Class")
par(op)

detach(package:statnet)
library("igraph")
library(intergraph)
iCon <- asIgraph(net_import)
coreness <- graph.coreness(iCon)
#table(coreness)
maxCoreness <- max(coreness)
Vname <- get.vertex.attribute(iCon,name='vertex.names',
                              index=V(iCon))
V(iCon)$name <- Vname
V(iCon)$color <- coreness + 1
V(iCon)$class <- as.vector(df_c_merged[,2])
  
colors <- rainbow(maxCoreness)
op <- par(mar=c(2,0,2,0))
plot(iCon,vertex.label=coreness,
     vertex.color=colors[coreness],
     main="Concepts colored by Coreness")
par(op)

ceb <- cluster_edge_betweenness(iCon)
cle <- cluster_leading_eigen(iCon)
cl <- cluster_louvain(iCon)
clp <- cluster_label_prop(iCon)
ci <- cluster_infomap(iCon)

mod_ceb <- modularity(ceb)
mod_cle <- modularity(cle)
mod_cl <- modularity(cl)
mod_clp <- modularity(clp)
mod_ci <- modularity(ci)

cl_levels = c(
  length(levels(as.factor(membership(cl)))),
  length(levels(as.factor(membership(cle)))),
  length(levels(as.factor(membership(ceb)))),
  length(levels(as.factor(membership(clp)))),
  length(levels(as.factor(membership(ci))))
)

cl_mod = c(mod_cl,mod_cle,mod_ceb,mod_clp,mod_ci)

cl_name = c("Louvain","Leading Eigen","Edge Betweenness","Label Prop","Infomap")

clbasic_df <- data_frame(
  algorithm = cl_name,
  levels = cl_levels,
  modularity = cl_mod
)

ggplot(clbasic_df, 
       aes(levels, modularity,
         shape = algorithm, colour = algorithm)) +
  geom_point() +
  labs(title = "# of clusters & modularity by algorithm")

cla <- as.numeric(as.factor(V(iCon)$class))
ceb_cl <- compare(ceb,cl,method="adjusted.rand")
cla_cl <- compare(cla,cl,method="adjusted.rand")
cla_ceb <- compare(cla,ceb,method="adjusted.rand")

com_out <- data_frame(
  name = c("Edge Betweenness x Louvain","Class x Louvin","Class x Edge Betweenness"),
  compare = c(ceb_cl,cla_cl,cla_ceb)
)
com_sort <- com_out %>% arrange(desc(compare))
com_sort <- com_sort %>% mutate(algorithm = factor(name,levels = name))
ggplot(com_sort,aes(algorithm,compare)) +
  geom_bar(stat="identity") +
  labs(title = "compare by algorithm") 
##### 

cluster_df <- data_frame(
  name = names(membership(cl)),
  class = V(iCon)$class,
  cl = as.vector(membership(cl)),
  cle = as.vector(membership(cle)),
  ceb = as.vector(membership(ceb)),
  clp = as.vector(membership(clp)),
  ci = as.vector(membership(ci))
)

cluster_group <- cluster_df %>% 
  group_by(cl,ceb) %>% 
  summarise(all_n = n()) %>% 
  arrange(desc(all_n))

cluster_cl <- cluster_df %>% 
  group_by(cl) %>% 
  summarise(cl_n = n()) %>% 
  arrange(desc(cl_n))

cluster_ceb <- cluster_df %>% 
  group_by(ceb) %>% 
  summarise(ceb_n = n()) %>% 
  arrange(desc(ceb_n))

cluster_cla <- cluster_df %>% 
  group_by(class) %>% 
  summarise(cla_n = n()) %>% 
  arrange(desc(cla_n))

cluster_cl_m <- cluster_group %>%
  left_join(cluster_cl,by="cl")

cluster_m <- cluster_cl_m %>%
  left_join(cluster_ceb,by="ceb")

cluster_m <- cluster_m %>% mutate(cl_ratio = all_n/cl_n)
cluster_m <- cluster_m %>% mutate(ceb_ratio = all_n/ceb_n)
cluster_m <- cluster_m %>% mutate(all_ratio = cl_ratio + ceb_ratio)
cluster_m <- cluster_m %>% mutate(label = paste(cl,"&",ceb))

### plot
all_n_threshold = 10
all_ratio_threshold = 1
ggplot(cluster_m, aes(all_ratio, all_n)) +
  geom_point() +
  geom_text(
    data=subset(cluster_m, 
                all_ratio >  all_ratio_threshold & 
                all_n > all_n_threshold),
    aes(all_ratio, all_n,label=label,colour="red")
  ) +
  labs(
    x = "Ratio",
    y = "Count",
    title = "Consistency between Edge Betweenness & Louvin"
    )
###

cluster_clacl <- cluster_df %>% 
  group_by(class,cl) %>% 
  summarise(clacl_n = n()) %>% 
  arrange(desc(clacl_n))

cluster_clacl_m <- cluster_clacl %>%
  left_join(cluster_cla,by="class")

cluster_clacl_m <- cluster_clacl_m %>%
  left_join(cluster_cl,by="cl")

cluster_clacl_m <- cluster_clacl_m %>% mutate(cla_ratio = clacl_n/cla_n)
cluster_clacl_m <- cluster_clacl_m %>% mutate(cl_ratio = clacl_n/cl_n)
cluster_clacl_m <- cluster_clacl_m %>% mutate(clacl_ratio = cla_ratio + cl_ratio)
cluster_clacl_m <- cluster_clacl_m %>% mutate(label = paste(substr(class,1,2),"&",cl))

### plot
clacl_n_threshold = 10
clacl_ratio_threshold = 1
ggplot(cluster_clacl_m, aes(clacl_ratio, clacl_n)) +
  geom_point() +
  geom_text(
    data=subset(cluster_clacl_m, 
                clacl_ratio >  clacl_ratio_threshold & 
                clacl_n > clacl_n_threshold),
    aes(clacl_ratio, clacl_n,label=label,colour="red")
  ) +
  labs(
    x = "Ratio",
    y = "Count",
    title = "Consistency between Class & Louvin"
    )
###

cluster_claceb <- cluster_df %>% 
  group_by(class,ceb) %>% 
  summarise(claceb_n = n()) %>% 
  arrange(desc(claceb_n))

cluster_claceb_m <- cluster_claceb %>%
  left_join(cluster_cla,by="class")

cluster_claceb_m <- cluster_claceb_m %>%
  left_join(cluster_ceb,by="ceb")

cluster_claceb_m <- cluster_claceb_m %>% mutate(cla_ratio = claceb_n/ceb_n)
cluster_claceb_m <- cluster_claceb_m %>% mutate(ceb_ratio = claceb_n/ceb_n)
cluster_claceb_m <- cluster_claceb_m %>% mutate(claceb_ratio = cla_ratio + ceb_ratio)
cluster_claceb_m <- cluster_claceb_m %>% mutate(label = paste(substr(class,1,2),"&",ceb))

### plot
claceb_n_threshold = 10
claceb_ratio_threshold = 1
ggplot(cluster_claceb_m, aes(claceb_ratio, claceb_n)) +
  geom_point() +
  geom_text(
    data=subset(cluster_claceb_m, 
                claceb_ratio >  claceb_ratio_threshold & 
                  claceb_n > claceb_n_threshold),
    aes(claceb_ratio, claceb_n,label=label,colour="red")
  ) +
  labs(
    x = "Ratio",
    y = "Count",
    title = "Consistency between Class & Edge Betweenness"
    )
###

cluster_3 <- cluster_df %>% 
  group_by(class,cl,ceb) %>% 
  summarise(all_n = n()) %>% 
  arrange(desc(all_n))

cluster_3_m <- cluster_3 %>%
  left_join(cluster_cla,by="class")

cluster_3_m <- cluster_3_m %>%
  left_join(cluster_ceb,by="ceb")

cluster_3_m <- cluster_3_m %>%
  left_join(cluster_cl,by="cl")

cluster_3_m <- cluster_3_m %>% mutate(cla_ratio = all_n/cla_n)
cluster_3_m <- cluster_3_m %>% mutate(ceb_ratio = all_n/ceb_n)
cluster_3_m <- cluster_3_m %>% mutate(cl_ratio = all_n/cl_n)
cluster_3_m <- cluster_3_m %>% mutate(all_ratio = cla_ratio + ceb_ratio + cl_ratio)
cluster_3_m <- cluster_3_m %>% mutate(label = paste(substr(class,1,2),"&",cl,"&",ceb))

### plot
all_n_threshold = 10
all_ratio_threshold = 1
ggplot(cluster_3_m, aes(all_ratio, all_n)) +
  geom_point() +
  geom_text(
    data=subset(cluster_3_m, 
                all_ratio >  all_ratio_threshold & 
                all_n > all_n_threshold),
    aes(all_ratio, all_n,label=label,colour="red")
  ) +
  labs(
    x = "Ratio",
    y = "Count",
    title = "Consistency among Class, Louvin and Edge Betweenness"
    )
###

center_df <- read.csv(file="MyCenter.csv",stringsAsFactors=FALSE)
cluster_m <- cluster_df %>% left_join(center_df, by = c("name" = "con"))
important_df <- cluster_m %>% 
  filter(cl==35 & ceb==6) %>%
  select(name,class,deg,bet)

ggplot(important_df, aes(deg,bet,fill=class,color=class)) +
  geom_point() +
  #facet_wrap(~cla) +
  labs(title = "35 & 6 Concepts measured by Deg & Bet") +
  geom_text(
    data=subset(important_df, deg > 10 | bet > 2500),
    aes(deg,bet,label=name),
    vjust = "inward", hjust="inward"
    )

iCon_m <- iCon %>% set_vertex_attr("ceb", value = membership(ceb))
iCon_m <- iCon_m %>% set_vertex_attr("cl", value = membership(cl))

subg <- subgraph(as.undirected(iCon_m),which((V(iCon_m)$cl==35) & (V(iCon_m)$ceb==6)))

rescale <- function(nchar, low, high){
  min_d <- min(nchar)
  max_d <- max(nchar)
  rscl <- ((high-low)*(nchar-min_d)) / (max_d-min_d)+low
  rscl
}

my_pal <- brewer.pal(10,"Paired")
classcat <- as.factor(V(subg)$class)
plot(subg,
     label=layout.kamada.kawai, 
     vertex.label=NA,
     vertex.color=my_pal[classcat],
     legend = TRUE,
     vertex.size=rescale(betweenness(subg),1,20))
legend("bottomleft",legend=levels(as.factor(V(subg)$class)),
       col=my_pal,pch=19, pt.cex=0.5, bty="n",cex=0.5,
       title="Concept Class")


library(knitr)
kable(important_df %>% arrange(desc(bet)), 
      caption = "35 & 6 Concepts Ordered by Betweenness")

important_df <- cluster_m %>% 
  filter(cl==30 & ceb==4) %>%
  select(name,class,deg,bet)

ggplot(important_df, aes(deg,bet,fill=class,color=class)) +
  geom_point() +
  #facet_wrap(~cla) +
  labs(title = "30 & 4 Concepts measured by Deg & Bet") +
  geom_text(
    data=subset(important_df, deg > 10 | bet > 2500),
    aes(deg,bet,label=name),
    vjust = "inward", hjust="inward"
    )

iCon_m <- iCon %>% set_vertex_attr("ceb", value = membership(ceb))
iCon_m <- iCon_m %>% set_vertex_attr("cl", value = membership(cl))

subg <- subgraph(as.undirected(iCon_m),which((V(iCon_m)$cl==30) & (V(iCon_m)$ceb==4)))

classcat <- as.factor(V(subg)$class)
plot(subg,
     label=layout.kamada.kawai, 
     vertex.label=NA,
     vertex.color=my_pal[classcat],
     legend = TRUE,
     vertex.size=rescale(betweenness(subg),1,20))
legend("bottomleft",legend=levels(as.factor(V(subg)$class)),
       col=my_pal,pch=19, pt.cex=0.5, bty="n",cex=0.5,
       title="Concept Class")


library(knitr)
kable(important_df %>% arrange(desc(bet)), 
      caption = "30 & 4 Concepts Ordered by Betweenness")

cl_subg_scatter <- function(i,cl_df){
    df <- cl_df %>% 
      filter(cl == i) %>%
      select(name,class,deg,bet)
    if(length(df$color > 1)){
      p <- ggplot(df, aes(deg,bet,fill=class,color=class))
    }else{
      p <- ggplot(df, aes(deg,bet))
    }
    p <- p +
      geom_point() +
      labs(title = paste("Louvin " ,i, " Concepts measured by Deg & Bet")) +
      geom_text(
        data=subset(df, deg > 10 | bet > 2500),
        aes(deg,bet,label=name),
        vjust = "inward", hjust="inward"
      )

      k <- kable(df %>% arrange(desc(bet)), 
          caption = paste("Louvin ", i,  " Concepts Ordered by Betweenness"))

      list(scatter = p, table = k)
}

cl_subg_plot <- function(i,g){
  subg <- subgraph(as.undirected(g),which((V(g)$cl==i)))
  classcat <- as.factor(V(subg)$class)
  my_pal <- brewer.pal(10,"Paired")
  p <- plot(subg,
      label=layout.kamada.kawai, 
      vertex.label=NA,
#      vertex.color=my_pal[classcat],
      legend = TRUE,
      vertex.size=degree(subg))
  p

#  legend("bottomleft",legend=levels(as.factor(V(subg)$class)),
#          col=my_pal,pch=19, pt.cex=0.5, bty="n",cex=0.5,
#          title="Concept Class")
}

for (i in 1:length(levels(as.factor(membership(cl))))){
  s <- cl_subg_scatter(i,cluster_m)
  cat('\n')
  print(s)
  cat('\n\n')
  p <- cl_subg_plot(i,iCon_m)
  print(p)
  cat('\n\n')
}

ceb_subg_scatter <- function(i,cl_df){
    df <- cl_df %>% 
      filter(ceb == i) %>%
      select(name,class,deg,bet)
    if(length(df$color > 1)){
      p <- ggplot(df, aes(deg,bet,fill=class,color=class))
    }else{
      p <- ggplot(df, aes(deg,bet))
    }
    p <- p +
      geom_point() +
      labs(title = paste("Edge Betweenness " ,i, " Concepts measured by Deg & Bet")) +
      geom_text(
        data=subset(df, deg > 10 | bet > 2500),
        aes(deg,bet,label=name),
        vjust = "inward", hjust="inward"
      )

      k <- kable(df %>% arrange(desc(bet)), 
          caption = paste("Edge Betweenness ", i,  " Concepts Ordered by Betweenness"))

    return(list(scatter = p, table = k))
}

ceb_subg_plot <- function(i,g){
  subg <- subgraph(as.undirected(g),which((V(g)$ceb==i)))
  classcat <- as.factor(V(subg)$class)
  my_pal <- brewer.pal(10,"Paired")
  p <- plot(subg,
      label=layout.kamada.kawai, 
      vertex.label=NA,
#      vertex.color=my_pal[classcat],
      legend = TRUE,
      vertex.size=degree(subg))
  return(p)

#  legend("bottomleft",legend=levels(as.factor(V(subg)$class)),
#          col=my_pal,pch=19, pt.cex=0.5, bty="n",cex=0.5,
#          title="Concept Class")
}

for (i in 1:length(levels(as.factor(membership(ceb))))){
  s <- ceb_subg_scatter(i,cluster_m)
  cat('\n')
  print(s)
  cat('\n\n')
  p <- ceb_subg_plot(i,iCon_m)
  print(p)
  cat('\n\n')
}



```

## Hypothesis
- Assumption
  1. Algorithms which show high modularity can form subgroups well.
  2. # and ratio of overlap between two clusters generated by two different algorithms can represent robustness of the cluster. 
  3. # and ratio of overlap between a concept class and a cluster can represent validity of a concept class.
- Result
1. "Louvin" and "Edge Betweenness" are the two algorithms which shows highest modularity score.
2. The cluster No.35 of Louvin and No.6 of Edge Betweenness is the highest # and ratio of overlap.
  - Center of this overlap is "working memory"
  - This subgroup are formed by mainly  Executive/Cognitive Control but including some other classes such as "Learning Memory", "Attention", and "NA".
3. The cluster No.30 of Louvin and No.4 of Edge Betweenness is the second highest # and ratio of overlap.
  - Center of this overlap includes mainly "perception" class with some "NA" concepts.
  - Center of this subgroup detected by betweeness centerality are perception, detection, and visual perception.

## Questions
1. What is modularity?
2. How does the "compare" function work?
3. Why are relations of some concepts blank?
4. How were the classes determined?
5. How were the class of concepts determined?
6. How can betweenness centrality between TM-based and Ontology-based be normalized?
7. Why are the closeness centrality of all concepts zero?
8. What is coreness?

## Goal at the moment
1. Cluster concepts by relations among concepts (done)
2. Classify concepts by relations among concepts 
3. Infer or verify relations by concept-task relation (MEASUREDBY value)

## Next Step
1. Investigate the theory of clustering algorithm and modularity
2. Interprete clusters
3. Exploring affiliation network to generate concept-task ties

## Next major task
1. merger algorithm of CA concepts to compare with TM-based betweenness



